Making Sequential Programs Deterministic

### 2019-03-22 design.tex
bullet points for design

\subsection{Maps discussion}
@Det --> keySet iteration is @Det
get(): can return o-nd collections

\subsection{Annotating more classes/providing more specifications}
Ease of annotating more JDk classes
User provided stub files to override existing behavior

>>>>

\subsection{Maps discussion}

\begin{itemize}
	\item A map is deterministic if the keySet() is deterministic.
	\item the iteration order of a keyset is the same as the iteration order of entrySet and Values.
	\item HashMap - can be @OrderNonDet or @NonDet.
	\item LinkedHashMap - can be @Det, @OrderNonDet, ot @NonDet.
	\item TreeMap - can be @Det or @NonDet.
	\item Problm with Map.get() : Annotating as @PolyDet is imprecise.
	\item We circumvent this by hardcoding rules to make it precise. (Describe the rule here)
	\item It was probably a bad design choice to make HashMap a subclass of Map (talk about how
	every method is overriden). Similarly for HashSet.
\end{itemize}

\subsection{Annotating more classes/providing more specifications}
\begin{itemize}
	\item Type system developer has to annotate methods in the JDK or any other library.
	\item Note: Another source of Nondeterminism we haven't analyzed: File system.
	\item Users can also provide stubs instead. (Steal some text from manual here)
\end{itemize}
